### 2016-08-09 2nd_round_comments/DVCS-CAN-Meeting-Comments.tex
update the answers

  \item Produce all 9 plots in right figure of slides 5 and 9 of \url{ 
     https://clasweb.jlab.org/rungroups/lowq/wiki/images/a/a0/ExcluCuts-CANeg6.pdf}   
     for a 2$\sigma$ and 1$\sigma$ cuts on missing $ep\gamma X$ M2.\\
     \textcolor{blue}{The coherent and the incoherent distributions are 
        presented in figure \ref{fig:exc_Coh} and \ref{fig:exc_InCoh} 
     respectively. No correlations were observed in the coherent DVCS channel, 
  while a slight correlation was observed between the $ep\gamma$ MM2 and $epX$ 
  MM2.} \textcolor{red}{Do we have to apply tighter cuts in the incoherent 
  case?.}
     \begin{figure}[tbp]
    \includegraphics[height=14.6cm]{fig/all_sigmas_coh_exc_cuts.pdf}
    \caption{Coherent exclusivity distributions corresponding to different cuts 
    on $e^{4}He\gamma X$ missing mass squared.}
    \label{fig:exc_Coh}
    \end{figure}                                                                  
    \begin{figure}[tbp]
    \includegraphics[height=14.6cm]{fig/all_sigmas_incoh_exc_cuts.pdf}
    \caption{ Incoherent exclusivity distributions for the different cuts on 
    $ep\gamma X$ missing mass squared.}
    \label{fig:exc_InCoh}
    \end{figure}

@@

\item Free proton asymmetries from FX's publication: implement a (possibly 3D/9 
points) interpolation to smooth out both statistical fluctuations and 
kinematical dependences. Reintroduce a corresponding section in the CAN. Take 
into account both stat. and syst. errors of both experiments in the ratio. The 
committee recommends though to be cautious about the statements on the 
asymmetry ratios in the future publication.

>>>>

  \item Produce all 9 plots in right figure of slides 5 and 9 of \url{ 
     https://clasweb.jlab.org/rungroups/lowq/wiki/images/a/a0/ExcluCuts-CANeg6.pdf}   
     for a 2$\sigma$ and 1$\sigma$ cuts on missing $ep\gamma X$ M2.\\
     \textcolor{blue}{The coherent and the incoherent distributions are 
        presented in figure \ref{fig:exc_Coh} and \ref{fig:exc_InCoh} 
     respectively. The reconstructed coherent and incoherent beam spin 
  asymmetries are presented in figures \ref{fig:exc_coh-alu} and 
  \ref{fig:exc_incoh-alu} respectively. In terms of the exclusivity 
  distributions, no correlations were observed in the coherent DVCS channel, 
  while a slight correlation was observed between the $ep\gamma$ MM2 and $epX$ 
  MM2.} \textcolor{red}{Do we have to apply tighter cuts in the incoherent 
  case?.}

  \begin{figure}[tbp]
    \includegraphics[height=14.6cm]{fig/all_sigmas_coh_exc_cuts.pdf}
    \caption{Coherent exclusivity distributions corresponding to different cuts 
    on $e^{4}He\gamma X$ missing mass squared.}
    \label{fig:exc_Coh}
    \end{figure}

    \begin{figure}[tbp]
       \centering
    \includegraphics[height=8.6cm]{fig/ALU_coherent_MM2.pdf}
    \caption{The integrated coherent beam-spin asymmetries as a function of 
    $\phi$ corresponding to different cuts on $e^{4}He\gamma X$ missing mass 
 squared.}
    \label{fig:exc_coh-alu}
    \end{figure}

    \begin{figure}[tbp]
    \includegraphics[height=14.6cm]{fig/all_sigmas_incoh_exc_cuts.pdf}
    \caption{ Incoherent exclusivity distributions for the different cuts on 
    $ep\gamma X$ missing mass squared.}
    \label{fig:exc_InCoh}
    \end{figure}

    \begin{figure}[tbp]
       \centering
    \includegraphics[height=8.6cm]{fig/ALU_incoherent_MM2.pdf}
    \caption{The integrated incoherent beam-spin asymmetries as a function of 
    $\phi$ corresponding to different cuts on $e^{4}He\gamma X$ missing mass 
 squared.}
    \label{fig:exc_incoh-alu}
    \end{figure}

@@

\item Free proton asymmetries from FX's publication: implement a (possibly 3D/9 
points) interpolation to smooth out both statistical fluctuations and 
kinematical dependences. Reintroduce a corresponding section in the CAN. Take 
into account both stat. and syst. errors of both experiments in the ratio. The 
committee recommends though to be cautious about the statements on the 
asymmetry ratios in the future publication.
  \begin{figure}[tbp]
    \includegraphics[height=14.6cm]{fig/ALU-proton-fits.png}
    \caption{ Fitting e1dvcs1 free proton beam-spin asymmetries. The dashed 
    curves are fits to the data in the form of 
 $p_{0}*(t-t_{min})*e^{p_{1}*\sqrt{t}}$, while the solid curves are from 
 calculations based on fitting the parameters $p_{0}$ and $p_{1}$.}
    \label{fig:free-proton-alu-fits}
    \end{figure}
